Figures

### 2016-08-17 ms_2_methods.Rmd
commit some changes. fuck. gonna make a conflict.

___short paragraph about other datasets we didn't include, i.e. SAUP?___

@@

__Comparison of taxonomic and regional distribution__:
To examine the overall taxonomic distribution across the spatial datasets (Fig. 1A), we grouped species by taxonomic class and data source, and determined the proportion of each class represented in each dataset.  We defined "paired map" species as those with spatial data in both datasets.

@@

__Comparison of paired maps__:
Using genus and species binomials as a matching key, we selected the "paired map" species - the subset of marine species that have range maps in both IUCN and AquaMaps current native distribution.  _We used the taxize package [@REF] in R [@REF] to standardize species names and synonyms; for species with separate subpopulation maps in IUCN, we combined all subpopulations to create a single global population._  ___To avoid double-counting, we removed subpopulations and species aliases. Used the taxize package? which version?___  We determined species presence within each spatial cell using the same criteria outlined above.

@@

_To highlight the differences in the datasets, we recalculated the OHI SPP status values using only one complete dataset at a time.  For the AquaMaps dataset, we used a presence threshold of 0% to align with the OHI 2016 assessment._  ___Fig. 3 compares these single-dataset scores to the 2016 OHI SPP status values.___

_To highlight the differences in the datasets, we selected the subset of species whose ranges are represented in both datasets, eliminating species found in only one or the other dataset.  In the original OHI SPP analysis, IUCN data was used to determine ranges for these overlapping species; we calculated all regional SPP status scores for just these species as our baseline.  We then recalculated the scores using AquaMaps ranges at a 40% presence threshold (as used in the original OHI analysis) and a 0% threshold (to better simulate the "limits of distribution" defined by IUCN maps) and compared them to our IUCN baseline._

_We then modified the original OHI source code to recalculate the 2015 SPP status scores for all regions and all species to examine the effects of changing the AquaMaps presence threshold from 40% to 0% (all range included), and the effects of changing the data source for the overlapping species from IUCN to AquaMaps.  We calculated the differences between these results and the published SPP status scores for 2015._

>>>>

___short paragraph about other datasets we didn't include, i.e. SAUP?  BOTW?___

@@

__Comparison of taxonomic and regional distribution__:
To examine the overall taxonomic distribution across the spatial datasets (Fig. 1A), we grouped species by taxonomic class and data source, and determined the proportion of each class represented in each dataset.

@@

__Comparison of paired maps__:
Using genus and species binomials as a matching key, we selected the "paired map" species - the subset of marine species that have range maps in both IUCN and AquaMaps current native distribution.  _We used the taxize package [@REF] in R [@REF] to standardize species names and synonyms; for species with separate subpopulation maps in IUCN, we combined all subpopulations to create a single global population._   For each of these paired map species, we determined species presence within each spatial cell for each dataset, using the same criteria outlined above.

@@

_To highlight the differences in the datasets, we recalculated the OHI SPP status values using only one complete dataset at a time.  For the AquaMaps dataset, we used a presence threshold of 0% to align with the OHI 2016 assessment.  Note that the OHI 2016 analysis includes the Birds of the World dataset in addition to IUCN and AquaMaps; we excluded it for our analysis._ ___Fig. 3 compares these single-dataset scores to the 2016 OHI SPP status values.___

~To highlight the differences in the datasets, we selected the subset of species whose ranges are represented in both datasets, eliminating species found in only one or the other dataset.  In the original OHI SPP analysis, IUCN data was used to determine ranges for these overlapping species; we calculated all regional SPP status scores for just these species as our baseline.  We then recalculated the scores using AquaMaps ranges at a 40% presence threshold (as used in the original OHI analysis) and a 0% threshold (to better simulate the "limits of distribution" defined by IUCN maps) and compared them to our IUCN baseline.~

~We then modified the original OHI source code to recalculate the 2015 SPP status scores for all regions and all species to examine the effects of changing the AquaMaps presence threshold from 40% to 0% (all range included), and the effects of changing the data source for the overlapping species from IUCN to AquaMaps.  We calculated the differences between these results and the published SPP status scores for 2015.~
